### 2016-09-08 rebuttal.txt

We try to provide a complete description of the method, but since we
are also distributing our implementation, it seems like a great idea
to do as you suggest.  Therefore we have added
installation/configuration instructions in Appendix A.

@@

> 2. The discussion of latency/timing is somewhat confusing, and I
> believe it omits what I (and other investigators) consider to be the
> most crucial metric of detection performance – the variation in
> latency from the onset of the targeted syllable to the firing of the
> TTL pulse.

We had extensively characterised the timing from the completion of the
target recognition region to the firing of the TTL pulse.  We have
tried to clean up those references and clarify our description: if the
detection point is at the onset of a syllable, then our results apply
(see the paragraph at line 361 in the manuscript, or the paragraph at
line 375 in the diff document).

@@

((1a)) That is correct, but the alignment does appear to be
sufficiently accurate:

We refer to this syllable-by-syllable adjustment to the alignment as
micro-realignment.  Even without that micro-realignment, jitter was
generally around 2 ms, as can be seen throughout Section 3.2,
especially Figs. 4-7.  Since this is well within the 10-ms window
suggested by the literature and indeed barely above the theoretically
optimal jitter given our detection parameters, we decided that the
improvement that could be achieved by micro-realigning song was
unimportant.

> So – please provide this measure where appropriate in Results. I
> suspect that the jitter measurements for real-time performance will
> not be much different with this metric than what is currently
> reported, but it would be very useful nonetheless.

We believe that we have provided a sufficient analysis of jitter, and
that, while the improvement you suggest could only decrease our jitter
measurement somewhat, the performance without that enhancement is
almost as good as it can be.

@@

> Line 189: It takes so long to train a network with just 2 to 4 hidden
> neurons?

Big data sets, and we made little effort to optimise offline
(training) speed!  But we changed the training algorithm and now
things are about 10 times faster.

> maybe reducing the training data would help (reduce the
> negative targets only).

To a first approximation, this contradicts your request that we add
cage noise, flapping, etc.  Luckily, training time shouldn't
matter--it's online performance that counts, right?  However, the
change to scaled conjugate gradient training has sped things up
considerably.

@@

> Line 203: How was Cn chosen?

Arbitrarily.  Now noted in the text.  Thanks.

> Line 201: gradient descent, not hillclimbing (on cost). cross
> validation.

My comment applied to either one, but that text, which just described
something we didn't do, was unnecessary, so I removed it.

@@

Some insight added, but we agree that it's a tool for a specific
community.  As is any tool.

> c) the training is done on around 3k song annotated and aligned and
> never provide the readers and potential user how to obtain such
> dataset.

((3a)) This is incorrect.  We cited the article in which alignment
software is described, and we linked to the alignment software.  The
only step that we have not described is using a recording device,
which is outside the scope of the paper.

> With my own experience on working with birds in social context, such
> dataset is extremely difficult to obtain without very invasive and
> constrained method.
>
> In the present manuscript, it has been obtained, presumably, by
> letting a bird to its own device in a small cage for hours to
> extract songs. Many experiments do not want such harsh treatment.

@@

> f) the experiment with Fibre Photometry is really nice but is a
> distraction from the main paper and brings nothing to the story

Right.  See (1c).

> g) very minor: its Levenberg (not Levenburg) and it is a very unusual
> choice here (usually some kind of enhanced backpropagation are used)
> probably related to the black-boxy nature of the matlab toolbox

Thanks!  It's a good point.  Levenberg-Marquardt is the default for
MATLAB's toolbox, and we wanted to use as many defaults as we could
(preserving the black-boxy nature of third-party tools as much as
possible in order to emphasise that the specific choice probably
doesn't really matter very much--hopefully any regression tool would
work roughly similarly!).  But it did turn out in the end that Scaled
Conjugate Gradient produced similar results faster.

### 2016-09-08 main.tex
Fix minor typos
Slightly nicer to reviewer 3.
Suggestions for editors.

This consistency allows a variety of experiments if precise moments in
song can reliably be detected quickly enough to trigger other
apparatus during singing.  A common area of study with this
song-triggering technique is the anterior forebrain pathway (AFP), a
homologue of mammalian basal ganglia consisting of a few distinct
brain areas concerned with the production and learning of song.  For
example, \cite{Kao2005} stimulated the lateral magnocellular nucleus
of the anterior nidopallium (LMAN)---the output nucleus of the
AFP---at precisely timed moments during song and showed that this area
repeatably controls specific variables in song output.
\cite{Wang2008interhemispheric} stimulated LMAN and the high vocal
centre (HVC) in one hemisphere or the other, and found that control of
song rapidly switches between hemispheres.  \cite{Keller2009}
investigated the response of cells in field L and the caudolateral
mesopallium during song with and without feedback perturbations as
well as external sounds, and concluded that these regions may hold a
representation of song against which auditory signals are compared.
\cite{Tumer2007pitchshift} played a disruptive sound during renditions
of a syllable that were slightly above (or below) its average pitch,
and showed that the presence of this apparently random natural
variability in songbird motor output is used to drive change in the
song.  \cite{Andalman2009} extended this experiment and showed that
AFP produces a corrective signal to bias song away from those
disruptions.  \cite{Charlesworth2011learning} showed that the song
change was isolated to within roughly 10 milliseconds (ms) of the
stimulus, and further proposed an elegant model that predicts the
shape of the learned response and suggests a simple mechanism.
\cite{Warren2011} showed that that AFP transfers the error signal to
the robust nucleus of the arcopallium (RA) using
NMDA-receptor--mediated glutamatergic transmission. By looking at song
recovery after applying the same pitch-shift paradigm,
\cite{Canopoli2014} showed that the caudal medial nidopallium is
implicated in memorising or recalling a recent song target, but for
neither auditory processing nor directed motor learning.

@@

\begin{enumerate}
\item Record and align a corpus of training songs.  The technique has been published in \cite{Poole2012}.
\item Choose one or more instants in the song that should create a trigger event, and train a
  neural network to recognise them. This step is carried out offline.  While any neural network software would produce equivalent results, we used MATLAB 2015b's neural network toolbox.
\item Once trained and saved, the neural network is used by a realtime
  detection program that listens to an audio signal and indicates detection of the target
  syllables via a TTL pulse.  We present three implementations, in MATLAB, LabVIEW, and Swift, that trade off hardware requirements, ease of maintenance, and performance.
\end{enumerate}
This method makes the following contributions:
\begin{itemize}
\item Fast: sub-millisecond latencies, with jitter around 2 ms.
\item Accurate: false positive rates under 0.001\% and false negative rates under 1\% for a variety of syllables.  Balancing these rates depends on a single relative-cost parameter.
\item State-of-the-art performance with default parameters.
\item Runs on inexpensive hardware.
\item Described in detail here, with reference implementations provided and benchmarked.
\end{itemize}

@@

We tested three implementations of the realtime detector.  For all of
these tests, we ran the detector processes under the operating
systems' default schedulers and process priorities, running typical
operating system daemon processes but no user loads.  The computers
had ample memory resources.

@@

      channels associated with the input. For each channel, select a the text-encoded version of 

@@

      {\tt Processor} class acts as a coordinator, receiving income audio, passing that

>>>>

This consistency allows a variety of experiments if precise moments in
song can reliably be detected quickly enough to trigger other
apparatus during singing.  A common area of study with this
song-triggering technique is the anterior forebrain pathway (AFP), a
homologue of mammalian basal ganglia consisting of a few distinct
brain areas concerned with the learning and production of song.  For
example, \cite{Kao2005} stimulated the lateral magnocellular nucleus
of the anterior nidopallium (LMAN)---the output nucleus of the
AFP---at precisely timed moments during song and showed that this area
repeatably controls specific variables in song output.
\cite{Wang2008interhemispheric} stimulated LMAN and the high vocal
centre (HVC) in one hemisphere or the other, and found that control of
song rapidly switches between hemispheres.  \cite{Keller2009}
investigated the response of cells in field L and the caudolateral
mesopallium during song with and without feedback perturbations as
well as external sounds, and concluded that these regions may hold a
representation of song against which auditory signals are compared.
\cite{Tumer2007pitchshift} played a disruptive sound during renditions
of a syllable that were slightly above (or below) its average pitch,
and showed that the presence of this apparently random natural
variability in songbird motor output is used to drive change in the
song.  \cite{Andalman2009} extended this experiment and showed that
AFP produces a corrective signal to bias song away from those
disruptions.  \cite{Charlesworth2011learning} showed that the song
change was isolated to within roughly 10 milliseconds (ms) of the
stimulus, and further proposed an elegant model that predicts the
shape of the learned response and suggests a simple mechanism.
\cite{Warren2011} showed that that AFP transfers the error signal to
the robust nucleus of the arcopallium (RA) using
NMDA-receptor--mediated glutamatergic transmission. By looking at song
recovery after applying the same pitch-shift paradigm,
\cite{Canopoli2014} showed that the caudal medial nidopallium is
implicated in memorising or recalling a recent song target, but for
neither auditory processing nor directed motor learning.

@@

\begin{enumerate}
\item Record and align a corpus of training songs.  The technique has been published in \cite{Poole2012}.
\item Choose one or more instants in the song that should create a trigger event, and train a
  neural network to recognise them. This step is carried out offline.  While any neural network software would produce equivalent results, we used MATLAB 2015b's neural network toolbox.
\item Once trained and saved, the neural network is used by a realtime
  detection program that listens to an audio signal and indicates detection of the target
  syllables via a TTL pulse.  We present three implementations, in MATLAB, LabVIEW, and Swift, that trade off hardware requirements, ease of maintenance, and performance.
\end{enumerate}
This method makes the following contributions:
\begin{itemize}
\item Fast: sub-millisecond latencies, with jitter around 2 ms.
\item Accurate: false negative rates under 1\% and false positive rates under 0.001\% for a variety of syllables.  Balancing these rates depends on a single relative-cost parameter.
\item State-of-the-art performance with default parameters.
\item Runs on inexpensive hardware.
\item Described in detail here, with reference implementations provided and benchmarked.
\end{itemize}

@@

We tested three implementations of the realtime detector.  For all of
these tests, we ran the detector processes under the operating
systems' default schedulers and process priorities, running typical
operating system daemon processes but no loads from user processes.
The computers had ample memory resources.

@@

      channels associated with the input. For each channel, select the text-encoded version of 

@@

      {\tt Processor} class acts as a coordinator, receiving incoming audio, passing that
